Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-17 chapters/introduction/introduction.tex
minor change

\subsection{Geo-Calibration}
%\todo{add deterministic methods}
%
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually the geo-calibration task is
straightforward: given an image, identify the time and the location it
was captured in the world and the direction the camera was facing.
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to environmental
monitoring~\cite{zhang2012mining}.
\todo{make it smoother}

\begin{itemize}[noitemsep]
\item \textbf{Geo-Localization:}
Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch \etal~\cite{doersch2012what} extract
location-dependent features that capture the relative appearance
differences of large cities.  Lin et al.~\cite{lin2013cross} localize
a ground-level image by learning the relationship between pairs of
ground and aerial images \footnote{In the context of our thesis, we
do not distinguish between the satellite imagery and the aerial
imagery} of the same location. Other techniques focus
on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

@@

\item \textbf{Camera Pose Estimation:}
\todo{}

@@

Automatic feature engineering has drawn a lot of attention over the
past years due to its ability to learn useful features without strong
expert knowledge about the data. Among many automatic feature
engineering approaches, deep neural networks are wildly accepted by
researchers as good tools to learn high-level image representations.
The most commonly used approach for deep feature learning is
full supervision, which usually requires manually annotated
data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Unfortunately, such data is not always available for certain tasks. 
In contrast, unlabeled data is offen plentiful (\ie cellphone photos
in Instagram or Youtube videos).

@@

\section{Our Approach}
Our approach consists of two big steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions which describe the fitness between the calibration
parameters and the images. As the second step of our approach, we
dismantle the full geo-calibration into several partial
geo-calibration tasks, each of which could provides a strong constraint
function that fits in the general model. The architecture of
our approaches refers to \figref{intro:architecture}.
%
In the end, we show that learning to geo-calibrate a camera is helpful
for high-level image feature extracting.

>>>>

\subsection{Geo-Calibration}
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. 
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to environmental
monitoring~\cite{zhang2012mining}.
Conceptually the geo-calibration task includes:
identifying the camera pose ({\em pose estimation}), the camera
geographic location ({\em geo-localization}), and the time the query
image was captured ({\em time estimation}).

\begin{itemize}[noitemsep]

\item \textbf{Pose Estimation:}
\newline

\item \textbf{Geo-Localization:}
Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch \etal~\cite{doersch2012what} extract
location-dependent features that capture the relative appearance
differences of large cities.  Lin et al.~\cite{lin2013cross} localize
a ground-level image by learning the relationship between pairs of
ground and aerial images \footnote{In the context of our thesis, we
do not distinguish between the satellite imagery and the aerial
imagery} of the same location. Other techniques focus
on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

@@

@@

Automatic feature engineering has drawn a lot of attention over the
past years. Compared to the manual feature engineering,
automatic feature engineering approaches are able to to learn useful
features without strong expert knowledge about the data. Among these
approaches, deep neural networks are wildly accepted by researchers as
good tools to learn high-level image representations.  The most
commonly used approach for deep feature learning is full supervision,
which usually requires manually annotated
data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Unfortunately, such data is not always available for certain tasks.
In contrast, unlabeled data is offen plentiful (\ie cellphone photos
in Instagram or Youtube videos).

@@

\section{Our Approach}

Our approach consists of two big steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions which describe the fitness between the calibration
parameters and the images. As the second step of our approach, we
dismantle the full geo-calibration into several partial
geo-calibration tasks, each of which could provides a strong constraint
function that fits in the general model. The architecture of
our approaches refers to \figref{intro:architecture}.
%
In the end, we show that learning to geo-calibrate a camera is helpful
for high-level image feature extracting.
